Applying the metallicity-dependent binary fraction to double white dwarf formation: \\ Implications for LISA

### 2022-08-30 src/tex/ms.tex
changed up text and switched around order of parameter variations in figures

\snotes{For binary systems leading to He + He DWDs, there are many more mergers for $\alpha25$ than for the fiducial \kb{model}. The lower CE efficiency \kb{\sout{entails} leads to DWD progenitor} mergers from \kb{failed CE ejection \sout{the binary failing to eject the CE}}, or \kb{the CE} shrinking the orbit such that it then merges on the second CE phase. Because\kb{\sout{, as discussed above,}} there are more \kb{\sout{very short-period} ZAMS binaries with orbital periods shorter than $10^4$ days} in F50, as the \kb{\sout{ZAMS binary}} population evolves there are more likely to be binary interactions in the population for F50 than FZ. This leads to more mergers in $\alpha25$ occurring for F50 before formation of the DWD and thus a lower formation efficiency overall for F50 in contrast to FZ. \kb{\sout{as we see} This is illustrated} in the $\alpha25$ He + He plot of Figure \ref{fig:form_eff}. Similar to the fiducial \kb{model}, a binary that becomes a He + He DWD at lower metallicities would merge before becoming one at higher metallicities because of the longer evolution timescales. These later interactions lead to closer post-CE separations and thus more mergers. The dip at [Fe/H]=$\sim -1.5\%$ stems from mergers before the DWD forms, \kb{again} similar to \kb{sout{for our}the } fiducial model. The peak that occurs in $\alpha25$ at $\sim 10\%$ Z$_\odot$ arises from binaries evolving faster \kb{\sout{(i.e.} and thus}} interacting earlier as metallicity increases. \kb{This means \sout{meaning}} that equivalent binaries that would have merged or formed a CO + He DWD instead at lower metallicities now survive \kb{\sout{into} to produce} a He + He \kb{DWD}. At higher metallicities, there are a higher proportion of wide\kb{\sout{-separation systems} ZMAS binaries}, which evolve off the Main Sequence too slowly to form a He + He DWD, causing the efficiency drop.

@@

\snotes{For CO + He binaries, there are again many more mergers for \kb{parameter variation} $\alpha25$ relative to the fiducial case. This is the \kb{\sout{dominating} dominant} way that \kb{progenitors do not evolve to produce DWDs \sout{binaries are lost}} at higher metallicities. At low metallicities \kb{\sout{we also see}} a number of \kb{\sout{systems} progenitor binaries} form CO + CO \kb{\sout{binaries} DWDs instead of He + CO DWDs}. \kb{\sout{-- t}T}his is especially the case in a ``Goldilocks zone" around log$_{10}$(Z/Z$_\odot$)sim -2, where RLO occurs late enough in \kb{a binary's} evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence \kb{\sout{why we see} producing} a dip in the formation efficiency. Because \kb{parameter variation} $\alpha5$ \kb{\sout{entails leads to}} less mergers due to the high CE efficiency, the formation efficiency is mostly governed by the metallicity-dependent ZAMS orbital period distribution. At higher metallicities the majority of \kb{\sout{lost systems} cases in model FZ where progenitors don't produce a CO + He DWD} are due to \kb{progenitor} mergers or to He + He \kb{\sout{binaries} DWDs} forming instead \kb{CO + He DWDs.} %due to the faster evolution at high metallicities and increasing radii inducing earlier binary interactions and hence stripping of both star's envelopes [$\leftarrow$ is this correct logic?]. I think this is already discussed above for fiducial so we don't need to worry about it.
At higher metallicities, the ZAMS orbital period distribution of FZ also drops below the \kb{orbital period} distribution \kb{\sout{for} of} F50 and extends out to orbital periods beyond what would form a CO + He. \kb{This causes \sout{ which is why}} the formation efficiencies for FZ and F50 \kb{to} cross at log$_{10}$(Z/Z$_\odot$)$\sim-0.5$. \kb{This is also apparent \sout{which we also see}} for the $q3$ variation, and to a lesser extent in the fiducial \kb{\sout{variation} case}.} %Any lost systems in $q3$ also is contributed to by: (i) some binaries at high metallicities not forming a CO + He DWD by present day due to envelope-stripping timescales being delayed by phases of stable mass transfer, (ii) mergers, and (ii) ONe + X DWDs forming instead.
\snotes{In $q3$, for any given orbital period we find that lower mass systems come from lower metallicities, which leads to an approximately constant formation efficiency.}

\snotes{For CO + CO, across all variations, very close \kb{ZAMS} binaries (P$_{\rm{orb}} \mathcal{O}(100$ days)) are lost at high metallicities when a binary that would form a CO + CO at low metallicities forms a CO + He or He + He DWD instead because the binary interacts before core Helium burning of one or both components. There are again many more mergers in $\alpha25$, and less mergers for $\alpha5$. Due to the high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods survive to become CO + CO DWDs rather than merging or becoming CO/He + He DWDs. There are many less mergers overall for $q3$ than all the $\alpha$ values because of the phase of stable mass transfer occurring before the CE phase rather than multiple CE phases, hence why the $q3$ efficiency is approximately constant across metallicity.}
\kb{**I think maybe another thing to point out is that the majority of CO + CO don't interact }

\snotes{[** Might need to fact check this paragraph **] The FZ curves for ONe + X are relatively similar amongst variations beyond height, and the loss of systems is the same as described for the fiducial simulation. We have more mergers once again for $\alpha25$, which lowers the F50 curve below FZ because F50 has the shortest-ZAMS-period end that FZ does not have. $\alpha5$ and $q3$ show F50 efficiencies with a very shallow slope due to the flat orbital period distribution, as well as due to less mergers overall.}

@@

Figure \ref{fig:CEsep} shows the average separation at the first instance of CE evolution, $a_{\text{CE}}$ of all DWD progenitors that result in systems orbiting in the LISA frequency band at present day, as a function of metallicity for each DWD type. The solid lines denote the average value, and the $1\sigma$ variance is shown in the surrounding shading. \snotes{We show this for our fiducial model and two of the binary parameter variations. For our fiducial, $\alpha25$ and $\alpha5$ models,} the average CE separation increases in general across metallicity. Higher-metallicity binaries will interact earlier in the binary's lifetime than a lower-metallicity binary of equal separation due to their relatively larger maximum radii. Since higher-metallicity binaries are also more likely to merge during CE interactions because of their relatively more massive donor envelopes, the DWDs which survive and eventually orbit in the LISA band originate from systems with higher interaction separations which allow their orbits to shrink significantly during CE phases without merging. This regulation plays a key role in smearing out any observable effects of a metallicity-dependent binary fraction in the population of DWDs observable by LISA. \snotes{The slope of the increase for these three models is dictated by the CE efficiency $\alpha$. With increasing metallicity there is a deepening of the convective envelope of the star compared to its lower metallicity counterparts at the same point in its evolution [is this the first time this idea is introduced? need to check], requiring more orbital energy to be available in order to eject the CE. Thus the high-metallicity binaries must have even wider separations for lower $\alpha$ values to ensure the binary does not merge before the envelope is ejected. We thus see a steeper separation slope for $\alpha25$, a less steep slope for $\alpha5$, and an intermediate slope for our fiducial model which has $\alpha=1$.}

\snotes{The DWDs in model $q3$ that survive into the LISA band at present day have different formation channels than those of our other three models. Most importantly, the first interaction of these binaries are \emph{not} a CE interaction, but rather a phase of stable mass transfer. Because of this, we do not include it in Figure \ref{fig:CEsep} because it does not reflect the binary interactions for these simulations. All the binaries in the other models have more than one instance of a CE phase during their evolution, and rarely undergo stable mass transfer. The systems in $q3$ by contrast typically undergo RLO followed by a phase of stable mass transfer as the binary's first interaction. During mass transfer the orbit first shrinks, and then will slightly widen once the binary's mass ratio flips. This process leads to formation of the first WD component. The companion is then formed later in the binary's evolution through a CE phase. Almost all systems in $q3$ undergo only a single CE phase. Of particular interest in $q3$ is the CO + He systems. All of the $q3$ CO + He binaries that end up in the LISA band have the Helium WD unexpectedly form first through stable mass transfer, with the CO WD forming second through a CE. These binaries tend to all have similar resulting orbital separations from mass transfer,  as can be seen by the relatively constant curve for CO + He's $\overline{a}_{\rm{CE}}$. There is still a slight increasing trend in CO + He (as well as CO + CO and a more pronounced trend in He + He) for $q3$ that stems from the metallicity-dependent convective envelope discussion above. We also see that the average interaction separation are overall lower for models $q3$ and $\alpha5$ than for the other two due to the orbital shrinkage that has already occured from stable mass transfer and the efficient CE phase that will lead to minimal orbital shrinkage respectively.}

\snotes{Strikeout: [\emph{Note that the average CE separation is close to the qualitative limit for close binaries of $P_{\rm{orb}}\gtrsim10^{4}\,\rm{day}$ for the CO + CO and ONe + X binaries. We investigated the fraction of close DWD progenitors which formed with orbital periods above this range for each DWD type. For the He + He DWDs, less than $10\%$ of all progenitors, regardless of metallicity originate in wide orbits. For CO + He population, the percentage increases from $10$--$15\%$ from low to high metallicities, and for the more massive CO + CO and ONe + X DWDs, the percentages increase from $15$--$25\%$ and $20$--$40\%$ respectively. This suggests that our application of the close binary fraction may not be valid over the entire range of the DWD progenitor population. However, since the relative sizes of CO + CO and ONe + X are small compared to the He + He and CO + He populations, we leave a further investigation of these effects to a future study.}] [$\leftarrow$ I think we can take out this whole paragraph since we now take this into account!]}

@@

There are two peaks in the distribution of He + He DWDs \snotes{which are most prominent in the fiducial and $\alpha25$ variations, and not as obvious for $\alpha5$ or $q3$. The prominent first peak in fiducial and $\alpha25$} occurs because near $Z\simeq 0.1Z_\odot$, the DWD formation efficiency transitions from near constant values to a sharp decrease (see Figure \ref{fig:form_eff}). However, for a drop in the formation efficiency by a factor of of $\sim$ six, the amount of star formation in galaxy \textbf{m12i} increases by more than an order of magnitude for supersolar metallicities. Above $Z=Z_\odot$ this overcompensates for the efficiency drop, producing the second peak. \snotes{For $\alpha5$ and $q3$, the lack of constraints on binary evolution -- from the increased CE efficiency in the former and increased propensity for stable mass transfer in the latter -- allow for less failed binaries from merging. This leads to less dramatic drops in formation efficiency across metallicity and thus suppressing the formation of two peaks in the number of LISA-band systems.}

\snotes{The $\alpha5$ and $q3$ variations have a higher number of F50 systems than FZ for all DWD types. This is due to the log-uniform P$_{\rm{orb}}$ distribution of F50 having more of the shortest-period binaries than the tails of the log-normal distribution of FZ, a discrepancy which becomes more significant with increasing metallicity as the FZ distribution moves from a peak of log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 3-4$ to log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 4-6$. This tail is less likely to survive to the LISA band at present day for the first two variations due to the harder binary evolution constraints. This is why we see essentially equal number of systems between FZ and F50 for the fiducial and $\alpha25$ variation: although the close binary fraction leads to a greater number of low-metallicity systems, this is compensated for by the FIRE distribution as well as the tendency for the shortest-period systems that F50 has a greater number of to merge, essentially washing out all differences between the populations.}

@@

\snotes{\sout{The reduced} A change in the} number of DWDs in model FZ relative to model F50 is also apparent in the GW PSD LISA will observe. We show the GW PSD of each model, as well as the confusion estimate, in Figure~\ref{fig:PSD}. While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50 \snotes{for $\alpha5$ and $q3$}. This is a direct consequence of the overall reduction in the size of the close DWD population in model FZ. \snotes{As we would expect, the foreground height remains unchanged for the fiducial and $\alpha25$ variations}.

Similar to previous studies, we find that LISA will be able to resolve several thousand DWDs. Figure \ref{fig:LISA_SNR} shows the amplitude spectral density vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the top and bottom rows show results for models FZ and F50 respectively. For comparison, we also show the LISA sensitivity curve, including the 
modeled confusion foreground from each population in black, and the the entire population for each model in grey. \snotes{Plots for our three parameter variations can be found in Appendix \ref{appendix:ASD_vars}.} Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models. The populations containing at least one He WD occupy the lower-ASD, higher-GW frequency region of parameter space compared to the total population, with CO + He DWDs having larger ASDs than the He + He DWD population. Conversely, DWD types without a He WD component tend to occupy the higher-ASD, lower-GW frequency region of parameter space. This difference is largely due to the formation scenario of DWDs containing a He WD, which form from the ejection of a common envelope created by the He WD progenitor. These lower mass progenitors overflow their Roche lobes at closer separations relative to the higher mass progenitors (e.g. Figure~\ref{fig:CEsep}) and thus also produce closer DWDs. While the distance to any one DWD strongly influences its ASD, DWD populations without a He WD component have, on average, higher ASDs due to their more massive WD components.

We note that the height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 2 for model FZ relative to model F50\snotes{ for variations $\alpha5$ and $q3$}, the number of resolved sources is not reduced to an equal degree. \snotes{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved. For the fiducial model and $\alpha25$ variation, the number of resolvable systems with SNR $>7$ do not change much (are reduced by 4.5\% and increased by 3\% respectively). However, $\alpha5$ sees a reduction in the number of resolvable systems by only 26\%, and $q3$ remains almost \emph{unchanged}, seeing a 1\% reduction, even though the overall LISA population of both variations is halved. A large portion of the maintenance of $q3$ is contributed to by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).} \snotes{[\emph{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.}][$\leftarrow$ moved to beginning of paragraph] Strikeout: [\emph{Between models FZ and F50, the number of resolvable systems with SNR $>7$ over all DWD types decreases by only $\sim14\%$.}]}

>>>>

\snotes{For binary systems leading to He + He DWDs, there are many more mergers for $\alpha25$ than for the fiducial \kb{model}. The lower CE efficiency \kb{\sout{entails} leads to DWD progenitor} mergers from \kb{failed CE ejection \sout{the binary failing to eject the CE}}, or \kb{the CE} shrinking the orbit such that it then merges on the second CE phase. Because\kb{\sout{, as discussed above,}} there are more \kb{\sout{very short-period} ZAMS binaries with orbital periods shorter than $10^4$ days} in F50, as the \kb{\sout{ZAMS binary}} population evolves there are more likely to be binary interactions in the population for F50 than FZ. This leads to more mergers in $\alpha25$ occurring for F50 before formation of the DWD and thus a lower formation efficiency overall for F50 in contrast to FZ. \kb{\sout{as we see} This is illustrated} in the $\alpha25$ He + He plot of Figure \ref{fig:form_eff}. Similar to the fiducial \kb{model}, a binary that becomes a He + He DWD at lower metallicities would merge before becoming one at higher metallicities because of the longer evolution timescales. These later interactions lead to closer post-CE separations and thus more mergers. The dip at [Fe/H]=$\sim -1.5\%$ stems from mergers before the DWD forms, \kb{again} similar to \kb{sout{for our}the } fiducial model. The peak that occurs in $\alpha25$ at $\sim 10\%$ Z$_\odot$ arises from binaries evolving faster \kb{\sout{(i.e.} and thus}} interacting earlier as metallicity increases. \kb{This means \sout{meaning}} that equivalent binaries that would have merged or formed a CO + He DWD instead at lower metallicities now survive \kb{\sout{into} to produce} a He + He \kb{DWD}. At higher metallicities, there are a higher proportion of wide\kb{\sout{-separation systems} ZAMS binaries}, which evolve off the Main Sequence too slowly to form a He + He DWD, causing the efficiency drop.

@@

\snotes{For CO + He binaries, there are again many more mergers for \kb{parameter variation} $\alpha25$ relative to the fiducial case. This is the \kb{\sout{dominating} dominant} way that \kb{progenitors do not evolve to produce DWDs \sout{binaries are lost}} at higher metallicities. At low metallicities \kb{\sout{we also see}} a number of \kb{\sout{systems} progenitor binaries} form CO + CO \kb{\sout{binaries} DWDs instead of He + CO DWDs}. \kb{\sout{-- t}T}his is especially the case in \kb{\sout{a ``Goldilocks zone" around} near} log$_{10}$(Z/Z$_\odot)\sim -2$, where RLO occurs late enough in \kb{a binary's} evolution that mass transfer remains stable and CO + CO's are formed rather than CO + He, hence \kb{\sout{why we see} producing} a dip in the formation efficiency. Because \kb{parameter variation} $\alpha5$ \kb{\sout{entails leads to}} less mergers due to the high CE efficiency, the formation efficiency is mostly governed by the metallicity-dependent ZAMS orbital period distribution. At higher metallicities the majority of \kb{\sout{lost systems} cases in model FZ where progenitors don't produce a CO + He DWD} are due to \kb{progenitor} mergers or to He + He \kb{\sout{binaries} DWDs} forming instead \kb{CO + He DWDs.}} %due to the faster evolution at high metallicities and increasing radii inducing earlier binary interactions and hence stripping of both star's envelopes [$\leftarrow$ is this correct logic?]. I think this is already discussed above for fiducial so we don't need to worry about it.
\snotes{At higher metallicities, the ZAMS orbital period distribution of FZ also drops below the \kb{orbital period} distribution \kb{\sout{for} of} F50 and extends out to orbital periods beyond what would form a CO + He. \kb{This causes \sout{ which is why}} the formation efficiencies for FZ and F50 \kb{to} cross at log$_{10}$(Z/Z$_\odot$)$\sim-0.5$. \kb{This is also apparent \sout{which we also see}} for the $q3$ variation, and to a lesser extent in the fiducial \kb{\sout{variation} case}.} %Any lost systems in $q3$ also is contributed to by: (i) some binaries at high metallicities not forming a CO + He DWD by present day due to envelope-stripping timescales being delayed by phases of stable mass transfer, (ii) mergers, and (ii) ONe + X DWDs forming instead.
\snotes{In $q3$, for any given orbital period we find that lower mass \kb{\sout{systems} DWDs originate \sout{come}} from lower metallicities,\kb{\sout{which leads} thus leading} to an approximately constant formation efficiency.}

\snotes{For CO + CO, across all variations, very close \kb{ZAMS} binaries (P$_{\rm{orb}} \mathcal{O}(100$ days)) at high metallicities} \kb{form a CO + He or He + He DWD instead of a CO + CO because the binary interacts before core Helium burning of one or both components. } 
%lost at high metallicities when a binary that would form a CO + CO at low metallicities forms a CO + He or He + He DWD instead 
There are again many more mergers in $\alpha25$, and \kb{\sout{less} fewer} mergers for $\alpha5$. Due to the high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods survive to become CO + CO DWDs rather than merging or becoming CO + He or He + He DWDs. There are \kb{\sout{less} fewer} mergers overall for $q3$ than all the $\alpha$ \kb{\sout{values} variations} because \kb{\sout{of the phase of stable mass transfer occurring before the CE phase} the first RLO occurrence leads to stable mass transfer from the primary to the secondary} rather than multiple CE phases. \kb{For both the $\alpha5$ and $q3$ variations, the majority of CO + CO DWDs originate in wide enough orbits that they don't interact before DWD formation. This leads to an approximately constant formation efficiency across metllicity in both cases.}

%\kb{This also leads to \kb\souce{hence why} \kb{an approximately constant formation efficiency} $q3$ \sout{efficiency}\kb{parameter variation} is approximately constant across metallicity.}
%\kb{**I think maybe another thing to point out is that the majority of CO + CO don't interact }

\kb{For model FZ, the ONe + X formation efficiencies follow similar trends aross each parameter variation. Their formation scenarios are similar to those described above for the fiducial binary evolution parameter set. The main difference between each parameter variation is only in the number of sources produced since the number of stellar mergers that occur before DWD formation increases with decreasing common envelope efficiency. In model F50, the formation efficiency is decreased significantly for parameter variation $\alpha25$ because the log-uniform orbital period distribution produces many ZAMS binaries with very short orbital periods which lead to stellar mergers during the CE phases.}

% Reworked this into the paragraph above.
%\snotes{[** Might need to fact check this paragraph **] The FZ curves for ONe + X are relatively similar amongst variations beyond height, and the loss of systems is the same as described for the fiducial simulation. We have more mergers once again for $\alpha25$, which lowers the F50 curve below FZ because F50 has the shortest-ZAMS-period end that FZ does not have. $\alpha5$ and $q3$ show F50 efficiencies with a very shallow slope due to the flat orbital period distribution, as well as due to less mergers overall.}

@@

Figure \ref{fig:CEsep} shows the average separation at the first instance of CE evolution, $a_{\text{CE}}$ of all DWD progenitors that result in systems orbiting in the LISA frequency band at present day, as a function of metallicity for each DWD type. The solid lines denote the average value, and the $1\sigma$ variance is shown in the surrounding shading. \snotes{We show this for our fiducial model and each of our binary parameter variations. For our fiducial, $\alpha25$ and $\alpha5$ parameter variations,} the average CE separation increases in general across metallicity. Higher-metallicity binaries will interact earlier in the binary's lifetime than a lower-metallicity binary of equal separation due to their relatively larger maximum radii. Since higher-metallicity binaries are also more likely to merge during CE interactions because of their relatively more massive donor envelopes, the DWDs which survive and eventually orbit in the LISA band originate from systems with higher interaction separations which allow their orbits to shrink significantly during CE phases without merging. This regulation plays a key role in smearing out any observable effects of a metallicity-dependent binary fraction in the population of DWDs observable by LISA. \snotes{The slope of the increase for these three models is dictated by the CE efficiency $\alpha$. With increasing metallicity there is a deepening of the convective envelope of the star compared to its lower metallicity counterparts at the same point in its evolution,} %[is this the first time this idea is introduced? need to check], \KB I think this is ok!
\snotes{requiring more orbital energy to be available in order to eject the CE. Thus the high-metallicity binaries must have even wider separations for lower $\alpha$ values to ensure the binary does not merge before the envelope is ejected. We thus see a steeper separation slope for $\alpha25$, a less steep slope for $\alpha5$, and an intermediate slope for our fiducial model which has $\alpha=1$.}

\snotes{The DWDs in model $q3$ that survive into the LISA band at present day have different formation channels than those of our other three \kb{\sout{models} parameter variations}. Most importantly, the first interaction of these binaries are \emph{not} a CE interaction, but rather a phase of stable mass transfer. \kb{\sout{Because of this, }} \kb{we show the CE phase which results from the second interaction for parameter variation $q3$} in Figure \ref{fig:CEsep}.}
% because it does not reflect the binary interactions for these simulations.} 
%All the binaries in the other models have more than one instance of a CE phase during their evolution, and rarely undergo stable mass transfer. 
\kb{In contrast to two CE phases for the fiducial, $\alpha25$ and $\alpha5$ parameter varitions, the DWD progenitors in parameter variation $q3$ typically undergo a phase of stable mass transfer as the binary's first interaction.} During mass transfer the orbit first shrinks, and then will slightly widen once the binary's mass ratio flips. This process leads to formation of the first WD component. The companion is then formed later in the binary's evolution through a CE phase. 
%Almost all systems in parameter variation $q3$ undergo only a single CE phase.

\snotes{Of particular interest in $q3$ is the CO + He systems. For all of the $q3$ CO + He binaries that \kb{\sout{end up} reside} in the LISA band \kb{at present}, the He WD \sout{unexpectedly} forms first through stable mass transfer, with the CO WD forming second through a CE. These binaries tend to all have similar resulting orbital separations from mass transfer, as can be seen by the relatively constant curve for CO + He's $\overline{a}_{\rm{CE}}$. There is still a slight increasing trend in CO + He (as well as CO + CO and a more pronounced trend in He + He) for $q3$ that stems from the metallicity-dependent convective envelope discussion above. We also see that the average interaction separation are overall lower for models $q3$ and $\alpha5$ than for the other two due to the orbital shrinkage that has already occured from stable mass transfer and the efficient CE phase that will lead to minimal orbital shrinkage respectively.}

%\snotes{Strikeout: [\emph{Note that the average CE separation is close to the qualitative limit for close binaries of $P_{\rm{orb}}\gtrsim10^{4}\,\rm{day}$ for the CO + CO and ONe + X binaries. We investigated the fraction of close DWD progenitors which formed with orbital periods above this range for each DWD type. For the He + He DWDs, less than $10\%$ of all progenitors, regardless of metallicity originate in wide orbits. For CO + He population, the percentage increases from $10$--$15\%$ from low to high metallicities, and for the more massive CO + CO and ONe + X DWDs, the percentages increase from $15$--$25\%$ and $20$--$40\%$ respectively. This suggests that our application of the close binary fraction may not be valid over the entire range of the DWD progenitor population. However, since the relative sizes of CO + CO and ONe + X are small compared to the He + He and CO + He populations, we leave a further investigation of these effects to a future study.}] [$\leftarrow$ I think we can take out this whole paragraph since we now take this into account!]} \kb{agreed!}

@@

There are two peaks in the distribution of He + He DWDs \snotes{which are most prominent in the fiducial and $\alpha25$ variations, and not as obvious for $\alpha5$ or $q3$. The prominent first peak in fiducial and $\alpha25$} occurs because near $Z\simeq 0.1Z_\odot$, the DWD formation efficiency transitions from near constant values to a sharp decrease (see Figure \ref{fig:form_eff}). However, for a drop in the formation efficiency by a factor of of $\sim$ six, the amount of star formation in galaxy \textbf{m12i} increases by more than an order of magnitude for supersolar metallicities. Above $Z=Z_\odot$ this overcompensates for the efficiency drop, producing the second peak. \snotes{For $\alpha5$ and $q3$, the lack of \kb{\sout{constraints on binary} dramatic orbital shrinking} -- from the increased CE efficiency in the former and increased propensity for stable mass transfer in the latter -- allow for less failed binaries from merging. This leads to less dramatic drops in formation efficiency across metallicity and thus suppressing the formation of two peaks in the number of LISA-band systems.}

\snotes{The $\alpha5$ and $q3$ variations \kb{\sout{have} produce} a higher number of F50 systems than FZ for all DWD types. This is due to the log-uniform P$_{\rm{orb}}$ distribution of model F50 having more of the shortest-period binaries than the tails of the log-normal distribution of FZ; a discrepancy which becomes more significant with increasing metallicity as the FZ distribution moves from a peak of log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 3-4$ to log$_{10}$(P$_{\rm{orb}}$/day)$\simeq 4-6$. This tail is less likely to survive to the LISA band at present for the \kb{\sout{first two} fiducial and $\alpha25$} variations due to the \kb{\sout{harder binary evolution constraints} increased propensity for mergers of DWD progenitors}. This \kb{\sout{is why we see essentially} effect produces an} equal number of systems between FZ and F50 for the fiducial and $\alpha25$ variations. \kb{In both cases, a}lthough the close binary fraction leads to a greater number of low-metallicity systems, this is compensated for by the FIRE \kb{star particle metallicity} distribution as well as the tendency for the shortest-period DWD progenitors \kb{in model} F50 to merge, essentially washing out all differences between the populations.}

@@

\snotes{\sout{The reduced} A change in the} number of DWDs in model FZ relative to model F50 is also apparent in the GW PSD LISA will observe. We show the GW PSD of each model, as well as the confusion forground estimate, in Figure~\ref{fig:PSD}. While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50 \snotes{for parameter variations $\alpha5$ and $q3$}. This is a direct consequence of the overall reduction in the size of the close DWD population in model FZ. \snotes{\sout{As we would expect, t}\kb{T}he foreground height remains unchanged for the fiducial and $\alpha25$ variations when comparing models FZ and F50}.

Similar to previous studies, we find that LISA will be able to resolve several thousand DWDs. Figure \ref{fig:LISA_SNR} shows the amplitude spectral density vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the top and bottom rows show results for models FZ and F50 respectively for the fiducial parameter variation. For comparison, we also show the LISA sensitivity curve, including the 
modeled confusion foreground from each population in black, and the the entire population for each model in grey. \snotes{Plots for our three parameter variations can be found in Appendix \ref{appendix:ASD_vars}.} Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models. The populations containing at least one He WD occupy the lower-ASD, higher-GW frequency region of parameter space compared to the total population, with CO + He DWDs having larger ASDs than the He + He DWD population. Conversely, DWD types without a He WD component tend to occupy the higher-ASD, lower-GW frequency region of parameter space. This difference is largely due to the formation scenario of DWDs containing a He WD, which form from the ejection of a common envelope created by the He WD progenitor. These lower mass progenitors overflow their Roche lobes at closer separations relative to the higher mass progenitors (e.g. Figure~\ref{fig:CEsep}) and thus also produce closer DWDs. While the distance to any one DWD strongly influences its ASD, DWD populations without a He WD component have, on average, higher ASDs due to their more massive WD components.

We note that the height of the confusion foreground and the number of DWDs radiating GWs with $f_{\rm{GW}} > 10^{-4}\,\rm{Hz}$ is reduced by a factor of 2 for model FZ relative to model F50\snotes{ for variations $\alpha5$ and $q3$}, the number of resolved sources is not reduced to an equal degree. \snotes{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved. For the fiducial and $\alpha25$ variations, the number of resolvable systems with SNR $>7$ \kb{\sout{do not change much}} are reduced by 4.5\% and increased by 3\% respectively. However, for $\alpha5$ the number of resolvable DWDs is reduced by only 26\%, and the number of resolvable DWDs $q3$ remains almost \emph{unchanged}, with a 1\% reduction even though the overall LISA population of both variations is halved. A large portion of the maintenance of the number of DWDs in parameter variation $q3$ is contributed to by He + He binaries with higher GW frequencies and lower ASDs which can now survive CE interactions due to an initial phase of mass transfer (see discussion of this formation channel in Section \ref{sec:CEsep}).}

%\snotes{[\emph{This is because in the absence of less competing GW signals from DWDs in the LISA frequency band, more DWDs can be individually resolved.}][$\leftarrow$ moved to beginning of paragraph] Strikeout: [\emph{Between models FZ and F50, the number of resolvable systems with SNR $>7$ over all DWD types decreases by only $\sim14\%$.}]}
